Methods for Analyzing Models of\\ Rod-Shaped Bacteria

### 2025-12-02 paper/main.tex
rework figure caption

\begin{figure}[H]
    \centering
    \includestandalone[width=0.8\textwidth]{figures/concept/overview}
    \caption{
        The project can be divided into subcomponents that interact with and depend on
        each other.
        Every component implicitly builds on the spatial representation of rod-shaped bacteria as
        vertices (see \nameref{subsec:spatial-representation}).
        Red boxes highlight the key scientific drivers of this study while yellow boxes indicate
        auxiliary methods.
        The blue box "Data Generation" displays a extension of this approach which is under active
        development.
    }
    \label{fig:flowchart-project-structure}
\end{figure}

>>>>

\begin{figure}[H]
    \centering
    \includestandalone[width=0.8\textwidth]{figures/concept/overview}
    \caption{
        Modular framework for parameter estimation of elongated bacteria.
        The individual components rely on a unified spatial representation (left) which discretizes
        bacteria into vertices (see \nameref{subsec:spatial-representation}).
        Building on top are visualization methods (top), a novel computational model for flexible
        elongated bacteria (middle) and data extraction routines (botom).
        Analysis methods (bottom, right) utilize extraction methods and can be informed by the model
        or used to guide modeling choices.
        These components can be combined to estimate the parameters of the developed computational
        model which can then be used in generating synthetic data (top, right).
        Colors indicate the componet type; core scientific drivers (red), auxiliary methods (yellow)
        and extensions (blue).
    }
    \label{fig:flowchart-project-structure}
\end{figure}
